Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections at the LArIAT experiment

### 2018-06-01 Chapter-5/5-Preparatory.tex
s

                                                  & MC $\pi^-$   & MC  $ \mu^-$ & MC  $e^-$ & MC  $\pi^-$ & MC  $\mu^-$ & MC  $e^-$  \\
\hline
&  &  &  & & &\\  
Total Initial events                     & 334500  & 334500 & 334500 &344500 &344500& 344500 \\
After Multiplicity Rejection        & 330668  & 333420 & 198065 &326576 &344208& 201380 \\
After WC2TPC Selection          & 218239  & 296333 & 91139  &230418 &300228& 98834  \\
Evts After Shower Rejection     & 208063  & 288914 &  20293 &219882 &293585& 17780  \\
&  &  &  & & &\\  
  \hline
&  &  &  & & &\\  
Selection Survival Rate           &62.2\% & 86.4\% & 6.1\% & 63.8\%& 85.2\%& 5.2\%\\
Beam Composition  @WC4      &  68.8\%   &  4.6 \%  & 26.6 \%    & 87.4 \% & 3.7 \%  & 8.9 \% \\ %
Expected Composition in XS sample &  88.5\%   & 8.2\%   & 3.3 \%   & 94.0\%	& 5.3\% & 0.7\%\\
                                                  &                      &                       &                   &                       &                        &\\  
\hline
\end{tabular}
\caption{MC selection flow per particle species.}
\label{tab:MCafterCutContaminants}
\end{table}

>>>>

                                                  & MC $\pi^-$   & MC  $ \mu^-$ & MC  $e^-$ & MC  $\pi^-$ & MC  $\mu^-$ & MC  $e^-$  \\
\hline
&  &  &  & & &\\  
Total Initial events                     & 334500  & 334500 & 334500 &344500 &344500& 344500 \\
After Multiplicity Rejection        & 330668  & 333420 & 198065 &326576 &344208& 201380 \\
After WC2TPC Selection          & 218239  & 296333 & 91139  &230418 &300228& 98834  \\
Evts After Shower Rejection     & 208063  & 288914 &  20293 &219882 &293585& 17780  \\
&  &  &  & & &\\  
  \hline
&  &  &  & & &\\  
Selection Survival Rate           &62.2\% & 86.4\% & 6.1\% & 63.8\%& 85.2\%& 5.2\%\\
Beam Composition  @WC4      &  68.8\%   &  4.6 \%  & 26.6 \%    & 87.4 \% & 3.7 \%  & 8.9 \% \\ %
Expected Composition&  88.5\%   & 8.2\%   & 3.3 \%   & 94.0\%	& 5.3\% & 0.7\%\\
                                    in XS sample               &                      &                       &                   &                       &                        &\\  
                                                  &                      &                       &                   &                       &                        &\\  
\hline
\end{tabular}
\caption{MC selection flow per particle species.}
\label{tab:MCafterCutContaminants}
\end{table}
